Numerical simulations of the Cordilleran ice sheet through the last glacial cycle

### 2016-01-25 cordillera-cycle.tex
Update tables to 0.05 K simulations.

    Vostok   &  78{\degree}28$^{\prime}$\,S   % 78.8
             & 106{\degree}50$^{\prime}$\,E   % 106.8
             & 3488
             & \chem{\delta^{18}O}
             & 0.75 & $-$6.0  % -7.9550
             & \citet{Petit.etal.1999} \\

    ODP~1012 &  32{\degree}17$^{\prime}$\,N
             & 118{\degree}23$^{\prime}$\,W
             & $-$1772
             & \chem{U^{K'}_{37}}
             & 1.61 & $-$6.1  % -3.7889
             & \citet{Herbert.etal.2001} \\

    ODP~1020 &  41{\degree}00$^{\prime}$\,N
             & 126{\degree}26$^{\prime}$\,W
             & $-$3038
             & \chem{U^{K'}_{37}}
             & 1.18 & $-$5.9  % -5.0000
             & \citet{Herbert.etal.2001} \\
    \bottomhline
\end{tabular}}
\end{table*}

@@

\begin{table*}
\caption{%
      Extremes in Cordilleran ice sheet grounded ice extent and sea-level
      relevant ice volume corresponding to
      MIS~4, 3 and 2 for each of the six low-resolution simulations
      (Fig.~\ref{fig:lr_ts}).}
\label{tab:extrema}
%\scalebox{.50}[.50]
{\begin{tabular}{l|ccc|ccc|ccc}
    \tophline
             & \multicolumn{3}{c|}{Age (ka)}
             & \multicolumn{3}{c|}{Ice extent (\unit{10^6\,km^2})}
             & \multicolumn{3}{c}{Ice volume (m\,s.l.e.)} \\
    Record   &  MIS~4 &  MIS~3 &  MIS~2
             &  MIS~4 &  MIS~3 &  MIS~2
             &  MIS~4 &  MIS~3 &  MIS~2 \\
    \middlehline
    GRIP     &  57.59 &  42.91 &  19.14
             &   1.93 &   0.67 &   2.09
             &   7.43 &   1.54 &   8.62 \\
    NGRIP    &  60.27 &  45.87 &  22.85
             &   2.13 &   0.73 &   2.11
             &   8.71 &   1.70 &   8.60 \\
    EPICA    &  61.90 &  52.40 &  17.36
             &   1.48 &   0.98 &   2.08
             &   4.84 &   2.55 &   8.56 \\
    Vostok   &  62.17 &  55.95 &  16.83
             &   1.52 &   1.04 &   2.17
             &   5.04 &   2.94 &   9.07 \\
    ODP 1012 &  56.91 &  47.69 &  23.10
             &   1.34 &   0.87 &   2.06
             &   4.10 &   2.20 &   8.40 \\
    ODP 1020 &  60.72 &  52.88 &  20.99
             &   1.21 &   0.69 &   2.06
             &   3.54 &   1.54 &   8.39 \\
    \cline{1-10}
    Minimum  &  56.91 &  42.91 &  16.83
             &   1.21 &   0.67 &   2.06
             &   3.54 &   1.54 &   8.39 \\
    Maximum  &  62.17 &  55.95 &  23.10
             &   2.13 &   1.04 &   2.17
             &   8.71 &   2.94 &   9.07 \\
    \bottomhline
\end{tabular}}
\end{table*}

>>>>

    Vostok   &  78{\degree}28$^{\prime}$\,S   % 78.8
             & 106{\degree}50$^{\prime}$\,E   % 106.8
             & 3488
             & \chem{\delta^{18}O}
             & 0.75 & $-$5.95  % -7.9550
             & \citet{Petit.etal.1999} \\

    ODP~1012 &  32{\degree}17$^{\prime}$\,N
             & 118{\degree}23$^{\prime}$\,W
             & $-$1772
             & \chem{U^{K'}_{37}}
             & 1.62 & $-$6.15  % -3.7889
             & \citet{Herbert.etal.2001} \\

    ODP~1020 &  41{\degree}00$^{\prime}$\,N
             & 126{\degree}26$^{\prime}$\,W
             & $-$3038
             & \chem{U^{K'}_{37}}
             & 1.21 & $-$6.05  % -5.0000
             & \citet{Herbert.etal.2001} \\
    \bottomhline
\end{tabular}}
\end{table*}

@@

\begin{table*}
\caption{%
      Extremes in Cordilleran ice sheet grounded ice extent and sea-level
      relevant ice volume corresponding to
      MIS~4, 3 and 2 for each of the six low-resolution simulations
      (Fig.~\ref{fig:lr_ts}).}
\label{tab:extrema}
%\scalebox{.50}[.50]
{\begin{tabular}{l|ccc|ccc|ccc}
    \tophline
             & \multicolumn{3}{c|}{Age (ka)}
             & \multicolumn{3}{c|}{Ice extent (\unit{10^6\,km^2})}
             & \multicolumn{3}{c}{Ice volume (m\,s.l.e.)} \\
    Record   &  MIS~4 &  MIS~3 &  MIS~2
             &  MIS~4 &  MIS~3 &  MIS~2
             &  MIS~4 &  MIS~3 &  MIS~2 \\
    \middlehline
    GRIP     &  57.59 &  42.91 &  19.14
             &   1.93 &   0.67 &   2.09
             &   7.43 &   1.54 &   8.62 \\
    NGRIP    &  60.27 &  45.87 &  22.85
             &   2.13 &   0.73 &   2.11
             &   8.71 &   1.70 &   8.60 \\
    EPICA    &  61.90 &  52.40 &  17.36
             &   1.48 &   0.98 &   2.08
             &   4.84 &   2.55 &   8.56 \\
    Vostok   &  62.21 &  55.87 &  16.86
             &   1.50 &   1.01 &   2.09
             &   4.94 &   2.81 &   8.57 \\
    ODP 1012 &  56.88 &  47.46 &  23.21
             &   1.36 &   0.90 &   2.13
             &   4.18 &   2.30 &   8.75 \\
    ODP 1020 &  60.37 &  52.72 &  20.41
             &   1.25 &   0.73 &   2.09
             &   3.66 &   1.65 &   8.62 \\
    \cline{1-10}
    Minimum  &  56.88 &  42.91 &  16.86
             &   1.25 &   0.67 &   2.08
             &   3.66 &   1.54 &   8.56 \\
    Maximum  &  62.21 &  55.87 &  23.21
             &   2.13 &   1.01 &   2.13
             &   8.71 &   2.81 &   8.75 \\
    \bottomhline
\end{tabular}}
\end{table*}
